Meta-analysis

### 2023-02-26 analysis/meta-analysis.Rmd
meta-analysis script and data updated

## Step 0 Obtaining data

calculate data from Jasmin et al. (2021) raw data

```{r}
Jasmin2021 <- read.csv(here("data", "meta-analysis", "Jasmin2021_data.csv"))
```

```{r}
Jasmin2021_filtered <- Jasmin2021 %>%
  filter(years_music <=3) %>%
  mutate(L1 = case_when(
    L1 %in% c("e", "E") ~ "E",
    TRUE ~ L1
  )) # Excluded participants with musical training more than 3 years 
```

```{r}
Jasmin2021_filtered %>%
  count(L1)
```

```{r}
Jasmin2021_filtered %>%
  group_by(L1) %>%
  summarise(dur_mean = mean(dur_thresh),
            dur_sd = sd(dur_thresh),
            pitch_mean = mean(pitch_thresh),
            pitch_sd = sd(pitch_thresh))
```

@@

```{r}
combine_lang <- function(data, study, measure, measure_overall, lang1, lang2, Tonal = T) {
  dat <- data %>%
    filter(Study == study) %>%
    filter(Measure == measure) %>%
    select(Tonal..n., Tonal.Mean, Tonal.SD)

  if(Tonal == F) {
    dat <- data %>%
      filter(Study == study) %>%
      filter(Measure == measure) %>%
      select(Comparison..N., Non.tonal.Mean, Non.tonal.SD)
  }

  name <- c("n1", "n2", "m1", "m2", "sd1", "sd2")
  values <- c(dat$Tonal..n., dat$Tonal.Mean, dat$Tonal.SD)

   if(Tonal == F) {
    values <- c(dat$Comparison..N., dat$Non.tonal.Mean, dat$Non.tonal.SD)
  }

@@

  if(Tonal){
    data <- data[-which(data$Study == study & data$Measure ==measure & data$Tonal_language == lang2),]
    data$Tonal..n.[which(data$Study == study & data$Measure ==measure)] <-   result$Npooled
    data$Tonal..n.[which(data$Study == study & data$Measure == measure_overall)] <- result$Npooled # updating the general task n
    data$Tonal.Mean[which(data$Study == study & data$Measure ==measure)] <- result$Mpooled
    data$Tonal.SD[which(data$Study == study & data$Measure ==measure)] <- result$SDpooled
    data$Tonal_language[which(data$Study == study & data$Measure ==measure)] <- paste0(lang1, " or ", lang2)
    data$Tonal_language[which(data$Study == study & data$Measure ==measure_overall)] <- paste0(lang1, " or ", lang2) # updating general task language
  }

  if(Tonal == F){
    data <- data[-which(data$Study == study & data$Measure ==measure & data$Comparison_language == lang2),]
    data$Comparison..N.[which(data$Study == study & data$Measure ==measure)] <-   result$Npooled
    data$Comparison..N.[which(data$Study == study & data$Measure == measure_overall)] <-   result$Npooled
    data$Non.tonal.Mean[which(data$Study == study & data$Measure ==measure)] <- result$Mpooled
    data$Non.tonal.SD[which(data$Study == study & data$Measure ==measure)] <- result$SDpooled
    data$Comparison_language[which(data$Study == study & data$Measure ==measure)] <- paste0(lang1, " or ", lang2)
    data$Comparison_language[which(data$Study == study & data$Measure ==measure_overall)] <- paste0(lang1, " or ", lang2)

@@

```{r}
meta_grouped$sd_pool <- sd_pooled(n1 = meta_grouped$Tonal..n., n2 = meta_grouped$Comparison..N., s1 = meta_grouped$Tonal.SD, s2 = meta_grouped$Non.tonal.SD)

@@

meta_grouped$total_n <- meta_grouped$Tonal..n. + meta_grouped$Comparison..N.

@@

```{r}
meta_grouped$se_smd <- se_smd(n1 = meta_grouped$Tonal..n., n2 = meta_grouped$Comparison..N., smd = meta_grouped$cohen_d)
meta_grouped$se_g <- se_smd(n1 = meta_grouped$Tonal..n., n2 = meta_grouped$Comparison..N., smd = meta_grouped$hedge_g)

@@

```{r}
# Chen 2016: Accuracy and raw score not 100% consistent (maybe due to excluding trials). Will calculate using accuracy bc it takes into account trial-excluding
meta_processed <- meta_processed %>%
  filter(!(Study == "Chen et al. (2016)" & Measure == "Melody subtest"))

#write.csv(meta_processed, here("data/meta-analysis", "meta_processed.csv"))
```

```{r}
 #write.csv(meta_processed, here("data/meta-analysis", "meta_processed_update.csv"))
# processed dataset before filtering out measures
```

## Step 4
```{r}
meta_processed <- read.csv(here("data/meta-analysis", "meta_processed_update.csv"))
```

@@

```{r}
meta_filtered <- meta_filtered %>%
  filter(Study != "Chang et al. (2016)") # removing this study as an outlier

meta_pooled <- meta_filtered %>%
  filter(Study != "Zhang et al. (2020)") # removing study comparing Japanese and Mandarin
```

```{r}
#write.csv(meta_pooled, here("data/meta-analysis",
         #                   "meta_processed_final.csv"))
```

```{r}
meta_processed_final <- read.csv(here("data/meta-analysis",
                            "meta_processed_final.csv"))
```

@@

```{r}
save(list = c("melodic.gen.random", "pitch.gen.random", "rhythm.gen.random", "study_num", "study_total_num"), file = here("results", "meta_analyses.RData"))
```

@@

meta_original %>%
  filter(Study %in% meta_processed_final$Study) %>%
  select(Study, Tonal..n.) %>%
  distinct(.) %>%
  pull(Tonal..n.) %>%
  sum() # total number of tonal participants analyzed 
```

>>>>

@@

```{r}
combine_lang <- function(data, study, measure, measure_overall, lang1, lang2, Tonal = T) {
  dat <- data %>%
    filter(Study == study) %>%
    filter(Measure == measure) %>%
    select(Tonal_N, Tonal.Mean, Tonal.SD)

  if(Tonal == F) {
    dat <- data %>%
      filter(Study == study) %>%
      filter(Measure == measure) %>%
      select(Non_tonal_N, Non.tonal.Mean, Non.tonal.SD)
  }

  name <- c("n1", "n2", "m1", "m2", "sd1", "sd2")
  values <- c(dat$Tonal_N, dat$Tonal.Mean, dat$Tonal.SD)

   if(Tonal == F) {
    values <- c(dat$Non_tonal_N, dat$Non.tonal.Mean, dat$Non.tonal.SD)
  }

@@

  if(Tonal){
    data <- data[-which(data$Study == study & data$Measure ==measure & data$Tonal_language == lang2),]
    data$Tonal_N[which(data$Study == study & data$Measure ==measure)] <-   result$Npooled
    data$Tonal_N[which(data$Study == study & data$Measure == measure_overall)] <- result$Npooled # updating the general task n
    data$Tonal.Mean[which(data$Study == study & data$Measure ==measure)] <- result$Mpooled
    data$Tonal.SD[which(data$Study == study & data$Measure ==measure)] <- result$SDpooled
    data$Tonal_language[which(data$Study == study & data$Measure ==measure)] <- paste0(lang1, " or ", lang2)
    data$Tonal_language[which(data$Study == study & data$Measure ==measure_overall)] <- paste0(lang1, " or ", lang2) # updating general task language
  }

  if(Tonal == F){
    data <- data[-which(data$Study == study & data$Measure ==measure & data$Comparison_language == lang2),]
    data$Non_tonal_N[which(data$Study == study & data$Measure ==measure)] <-   result$Npooled
    data$Non_tonal_N[which(data$Study == study & data$Measure == measure_overall)] <-   result$Npooled
    data$Non.tonal.Mean[which(data$Study == study & data$Measure ==measure)] <- result$Mpooled
    data$Non.tonal.SD[which(data$Study == study & data$Measure ==measure)] <- result$SDpooled
    data$Comparison_language[which(data$Study == study & data$Measure ==measure)] <- paste0(lang1, " or ", lang2)
    data$Comparison_language[which(data$Study == study & data$Measure ==measure_overall)] <- paste0(lang1, " or ", lang2)

@@

```{r}
meta_grouped$sd_pool <- sd_pooled(n1 = meta_grouped$Tonal_N, n2 = meta_grouped$Non_tonal_N, s1 = meta_grouped$Tonal.SD, s2 = meta_grouped$Non.tonal.SD)

@@

meta_grouped$total_n <- meta_grouped$Tonal_N + meta_grouped$Non_tonal_N

@@

```{r}
meta_grouped$se_smd <- se_smd(n1 = meta_grouped$Tonal_N, n2 = meta_grouped$Non_tonal_N, smd = meta_grouped$cohen_d)
meta_grouped$se_g <- se_smd(n1 = meta_grouped$Tonal_N, n2 = meta_grouped$Non_tonal_N, smd = meta_grouped$hedge_g)

@@

```{r}
# Chen 2016: Accuracy and raw score not 100% consistent (maybe due to excluding trials). Will calculate using accuracy bc it takes into account trial-excluding
meta_processed <- meta_processed %>%
  filter(!(Study == "Chen et al. (2016)" & Measure == "Melody subtest"))
```

```{r}
classification <- read.csv(here("data/meta-analysis", "Measure_classification.csv"))

meta_processed <- full_join(meta_processed, classification) %>%
  distinct(.)
```

## Step 4

@@

```{r}
#meta_filtered <- meta_filtered %>%
#  filter(Study != "Chang et al. (2016)") # removing this study as an outlier

meta_processed_final <- meta_filtered %>%
  filter(Study != "Zhang et al. (2020)") # removing study comparing Japanese and Mandarin
```

@@

```{r}
#save(list = c("melodic.gen.random", "pitch.gen.random", "rhythm.gen.random", "study_num", "study_total_num"), file = here("results", "meta_analyses.RData"))
```

@@

meta_original %>%
  filter(Study %in% meta_processed_final$Study) %>%
  select(Study, Tonal_N) %>%
  distinct(.) %>%
  pull(Tonal_N) %>%
  sum() # total number of tonal participants analyzed 
```
